%-------------------------
% thank you to the following person
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{geometry}
\geometry{
    left=0.5in,
    right=0.5in,
    top=0.5in,
    bottom=0.5in,
}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% You can choose your preferred font here.

% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
% Not Necessary Here

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Sajih Bin Suja} \\ \vspace{1pt}
    25/D, Shukrabad, Dhaka-1207, Bangladesh \\ \vspace{1pt}
    \small \textbar\ \href{mailto:sajih.binsuja5@gmail.com}{sajih.binsuja5@gmail.com} \hfill \textbar\ \href{https://linkedin.com/in/sajih538/}{linkedin.com/in/saih538} \hfill \textbar\ \href{https://github.com/kukkurukku}{github.com/kukkurukku}
    \vspace{-8pt}
\end{center}

%------RESEARCH INTERESTS-------
\section{Research Interests}
{Fluid Mechanics, CFD, Multiphase Flows, Porous Media, Thermal Management}

%-----------EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Walton Hi-Tech Industries PLC.}{August 2023 -- Present}
{Simulation Engineer -- Department of Research \& Innovation -- Residential Air Conditioner}{Gazipur, Bangladesh}
\resumeItemListStart
\resumeItem{Optimization and engineering design of centrifugal blowers and axial exhaust fans.}
\resumeItem{Conduct computational and performance analyses of indoor and outdoor units, augmented by reliability and transportation testing to ensure optimal air conditioner functionality.}
\resumeItem{CAD-based design, prototyping and fitting assessments of air-conditioner components. }
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-16pt}
%-----------EXPERIENCE-----------
\section{Research Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Computational Fluid Dynamics Lab, KUET}{2020 -- 2023}
{Research Assistant}{Khulna, Bangladesh}
\resumeItemListStart
\resumeItem{Numerical analysis on porous metal foam for thermal management of high heat flux systems.}
\resumeItem{Investigating swirling jets through numerical studies.}
\resumeItem{Researched impact of high heat flux and thermal management of electrical components.}
\resumeItem{Numerical computations on non-premixed methane-oxygen jet for metal melting.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-16pt}

\section{Publications}
\begin{itemize}[leftmargin=0in, label={}]
{\item{\textbf{Journal Publications}}}
\resumeItemListStart
\resumeItem{\textbf{Suja, S.B.}, Pranto, M.R.I. and Ahmed, Z.U., "Swirling Jet Impingements for Thermal Management of High Concentrator Solar Cells Using Nanofluids." 
\textit{International Journal of Thermofluids}, Volume 19C (2023), 100387.}
ISSN 2666-2027. DOI: \url{https://doi.org/10.1016/j.ijft.2023.100387}.
\resumeItemListEnd
\vspace{-2pt}

{\item{\textbf{Conference Proceedings}}}
\resumeItemListStart
\resumeItem{\textbf{Suja, S.B.}, Pranto, M.R.I. and Ahmed, Z.U., "Numerical Analysis of Swirling Jet Impingements for Thermal Management of HCPV using Nanofluids." 
In \textit{ICMIEE 2022: International Conference of Mechanical, Industrial \& Energy Engineering}, Khulna, 22-24 December.}
\resumeItem{Alam, S.I., \textbf{Suja, S.B.}, and Islam, M.S., "Influence of Venturi on Heat Transfer Characteristics of Nanofluids Flowing Across Pipe." 
In \textit{ICMERE 2021: International Conference of Mechanical Engineering and Renewable Energy}, Chittagong, 12-14 December.}
\resumeItem{\textbf{Suja, S.B.}, Pranto, M.R.I., Turna, R.N. and Ahmed, Z.U., "Conjugate Heat Transfer Analysis of Different CPU Cooling Processes Using Computational Fluid Dynamics." 
In \textit{ICMIEE 2020: International Conference of Mechanical, Industrial \& Energy Engineering}, Khulna, 19-21 December.}
\resumeItemListEnd
\end{itemize}

\section{Academic Credentials}
\resumeSubHeadingListStart
\resumeSubheading
{Khulna University of Engineering \& Technology}{2017 -- 2022}
{Bachelor of Science in Mechanical Engineering}{Khulna, Bangladesh}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{CGPA}{-- 3.13/4.00} \\
}}
\end{itemize}
\resumeSubHeadingListEnd

\section{Standardized Tests}
\begin{itemize}[leftmargin=0in, label={}]
{\item{
\textbf{Graduate Record Examination (GRE)} \\Total Score – 324/340, Quantitative Reasoning – 170/170, Verbal Reasoning – 154/170, Analytical Writing Assessment – 4.0/6.0.\\
Date Taken: November 3rd, 2022
}}
{\item{
{\textbf{International English Language Testing System (IELTS)}\\
Overall Band Score – 8.0, Speaking – 8.0, Reading – 9.0, Listening – 9.0, Writing – 6.5.\\
Date Taken: December 4th, 2022}}}
\end{itemize}

\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
{\item{
\textbf{CAD}{: SOLIDWORKS, Fusion 360} \\
\textbf{CAE}{: ANSYS FLUENT, ANSYS CFX, Star-CCM+, OpenFOAM, SIMULIA Abaqus, ANSYS Mechanical, LS-Dyna} \\
\textbf{Languages}{: Python, MATLAB, C} \\
\textbf{Graphics and Rendering}{: KeyShot, Illustrator, Photoshop, Blender 2.9} \\
}}
\end{itemize}
\vspace{-16pt}

\section{Certifications}
\begin{itemize}[leftmargin=0.15in]
\item {\textbf{Certified SolidWorks Associate (CSWA)}} – Issued by Dassault Systèmes.
\item \textbf{Online Courses}
\begin{itemize}
\item ENGR2000X: A Hands-on Introduction to Engineering Simulations – Cornell University (edX).
\item Excel Skills for Business – Macquarie University (Coursera).
\item Python for Everybody – University of Michigan (Coursera).
\item MATLAB Programming for Engineers and Scientists – Vanderbilt University (Coursera).
\end{itemize}
\end{itemize}

\section{Technical Presentation}
\begin{itemize}
\item Pranto, M. R. I., \textbf{Suja, S. B.}, “Smart and Eco-friendly E-waste recycling system”, Mechanical Festival Poster Presentation, Department of Mechanical Engineering, Khulna University of Engineering \& Technology, Khulna, September 2019.
\end{itemize}

\section{Awards}
\begin{itemize}
\item Finalist – Aer-O-Vacx Segment – Cognizance at Indian Institute of Technology (IIT), Roorkee, 2021.
\item Third Place – Poster Presentation – Mechanical Festival at Department of Mechanical Engineering, KUET, 2019.
\item Runners Up - KUET Inter Department Soccer, 2017-18 Season.
\end{itemize}

%-----------INVOLVEMENT---------------
\section{Extracurricular Activities}
\begin{itemize}
\item Organized workshops on Computational Fluid Dynamics and "Speak Out For Engineering – SOFE, Khulna Regional Heat" as Assistant General Secretary of IMechE KUET Student Chapter.
\item Led a team of four as Executive (Graphics \& Content) for Ignition 2019, a national mechanical festival by KUET's Mechanical Engineering Department.
\item Manager (Student) of KUET Mechanical Department Soccer team.
\end{itemize}

\section{References}
\begin{minipage}[t]{0.45\textwidth}
\textbf{Dr. Zahir Uddin Ahmed} \\
Professor \\
Department of Mechanical Engineering, KUET \\
E-mail: \href{mailto:zuahmed@me.kuet.ac.bd}{zuahmed@me.kuet.ac.bd}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\textbf{Dr. Md. Ashraful Islam} \\
Professor \\
Department of Mechanical Engineering, KUET \\
E-mail: \href{mailto:md.islam@me.kuet.ac.bd}{md.islam@me.kuet.ac.bd}
\end{minipage}

\begin{minipage}[t]{0.45\textwidth}
\textbf{Dr. Mohammad Ilias Inam} \\
Professor \\
Department of Mechanical Engineering, KUET \\
E-mail: \href{mailto:iliasinam@me.kuet.ac.bd}{iliasinam@me.kuet.ac.bd}
\end{minipage}

\end{document}
